\clearpage
%\section{Abstract}
%This document is a comprehensive report about the status of single-dish continuum observations with ALMA...BlaBla...

%\clearpage
\section{Introduction}
\thispagestyle{fancy}


\subsection{Purpose}
This document reports verifications of correlation processing for the 7m-array observations using the 64-input correlator (also known as BLC).

Currently, as of Cycle 9, the ACA correlator (ACAC) is used for the Morita array (the 7m array and the TP array) processing. Since Cycle 10, the ACA spectrometer (ACASPEC) is planned to take over the spectroscopy processing for the TP array and the ACAC will dedicates to 7m-array correlation.
The BLC is also capable to perform subarray correlations for the 12m array and the 7m array, in parallel, when the ACAC is out of service. This 7m-array correlation using the BLC is a contingency plan for troubles or future decommission plan of the ACAC.

To validate the BLC correlation of the 7m array for science operations, we have carried out commissioning science verification (CSV) activities. Here we present the results of the CSV.


%\begin{tabular}{|p{1.0cm}|p{6.5cm}|p{6.8cm}|}
\subsection{Applicable documents}
The following documents are part of this document to the extent specified herein.
If not explicitly stated otherwise, the latest issue of the document is valid.\\
\begin{tabular}{|p{1.2cm} | p{8.5cm} | p{4.5cm}|}
\hline
\rowcolor{gray} \bf Appl. & \bf Document Title &\bf Doc.\\
\hline
$[$AD01$]$ &ACA Spectrometer Technical Specifications and Requirements   					& \href{http://edm.alma.cl/forums/alma/dispatch.cgi/iptdocscorr/showFile/101189/d20210529211811/Yes/2021-04-09-ALMA-64.00.00.00-005-C-SPE-ACA_Spectrometer+Technical+Specifications.pdf}{ALMA-64.00.00.00-0005-B-SPE} \\
$[$AD02$]$ &ACA Spectrometer Assembly, Transportation, Integration and Verification Plan  	& \href{http://edm.alma.cl/forums/alma/dispatch.cgi/iptdocscorr/docProfile/101235/d20191209084810}{CORL-64.00.00.00-0022-A-PLA} \\
$[$AD03$]$ &ACA Spectrometer Subsystem Design Description   								& \href{http://edm.alma.cl/forums/alma/dispatch.cgi/iptdocscorr/docProfile/101230/d20200610070519}{CORL-64.00.00.00-0008-A-DSN} \\
$[$AD04$]$ &Report on Dynamic Range, Nonlinearity Correction and Delay Correction Implemented into the ACA Spectrometer  & \href{http://edm.alma.cl/forums/alma/dispatch.cgi/iptdocscorr/docProfile/101273/d20200825044738/No}{CORL-64.00.00.00-0028-A-REP} \\
$[$AD05$]$ &ACA spectrometer Commissioning and Science Verification Plan  & \href{http://edm.alma.cl/forums/alma/dispatch.cgi/iptdocscorr/docProfile/101273/d20200825044738/No}{CORL-64.00.00.00-0028-A-REP} \\
\hline
\end{tabular}

\subsection{Reference documents}
The following documents contain additional information and can be referenced in this document.\\
\begin{tabular}{|p{1.2cm} | p{8.5cm} | p{4.5cm}|}
\hline
\rowcolor{gray} \bf Ref. & \bf Document Title &\bf Doc.\\
\hline
$[$RD01$]$ & ALMA System Technical Requirement &  \href{}{ALMA-80.04.00.00-005-C-SPE} \\
\hline
\end{tabular}

%\subsection{Acronyms}
%For a complete set of acronyms and abbreviations used in the ALMA project, please go to the Acronym Finder [AD01].

\clearpage
